Constraints on Assembly Bias from Galaxy Clustering

### 2016-05-23 ms.tex
Changed author Prince R. Nelson to P. Rogers Nelson

\author[Zentner et al.]
{Andrew R. Zentner$^{1}$, Andrew P. Hearin$^{2}$, Frank C. van den Bosch$^{3},$ \newauthor
Antonio Villareal$^{1}$, Johannes Lange$^{3}$, Prince R. Nelson$^{4}$, Probably some others of unspecified origin\\ \\
$^1$Department of Physics and Astronomy \& Pittsburgh Particle Physics, Astrophysics, and Cosmology Center (PITT PACC),\\ University of Pittsburgh, Pittsburgh, PA 15260\\
$^2$Yale Center for Astronomy \& Astrophysics, Yale University, New Haven, CT\\
$^3$Department of Astronomy, Yale University, P.O. Box 208101, New Haven, CT\\
$^4$Paisley Park, Chanhassen, MN\\
}

>>>>

\author[Zentner et al.]
{Andrew R. Zentner$^{1}$, Andrew P. Hearin$^{2}$, Frank C. van den Bosch$^{3},$ \newauthor
Antonio Villareal$^{1}$, Johannes Lange$^{3}$, P. Rogers Nelson$^{4}$, Probably some others of unspecified origin\\ \\
$^1$Department of Physics and Astronomy \& Pittsburgh Particle Physics, Astrophysics, and Cosmology Center (PITT PACC),\\ University of Pittsburgh, Pittsburgh, PA 15260\\
$^2$Yale Center for Astronomy \& Astrophysics, Yale University, New Haven, CT\\
$^3$Department of Astronomy, Yale University, P.O. Box 208101, New Haven, CT\\
$^4$Paisley Park, Chanhassen, MN\\
}
